Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 paper_enahpc14/Sec3:Environment-setup.tex
Manuel's changes

\begin{itemize}
\item \monch is a 10 rack NEC-provided cluster composed
  of 312 compute  nodes %and utilized by members  of the Swiss Platform
  %for Advanced Scientific  Computing (PASC) project~\citep{PASC}
   at CSCS. Each
  node comprises two Intel Ivy Bridge EP  E5-2660 ten-core processors
  operating at  2.2 GHz, equipped with 32\,GB of DDR3 1600\,MHz  RAM and connected  via InfiniBand Mellanox  SX6036 and FDR switches. For our  experiments, 
  a full rack constituted of 52 nodes was used. \monch is  slated to stay
  in  service  without  hardware  upgrade  for  the  duration  of  the
  Exa2Green  project,  allowing   an  identical  configuration  to  be
  recreated for future assessments of the baseline.\\

\item \pilat is a dual-socket eight-core Intel Sandy
  Bridge EP based cluster composed of 42 compute nodes %and used as Piz Daint pre-post  processing cluster 
  at  CSCS.  The 2 login  nodes and
  the 42 computes nodes consists in 11 twin-pair Intel E5-Series DALCO
  r2264i4t 2U scalable compute modules. Each module contains 4 compute
  nodes based  on two Intel Xeon E5-2670 processors operating  at 2.6\,GHz equipped with 64GB of DDR3 1600\,MHz RAM and connected  via InfiniBand Mellanox SX6036 and FDR switches. 
  For our  experiments, a  full rack constituted  of 42 standard  compute nodes
  was used. \pilat  is based  on  Intel's second-generation
  processors, conventional in  HPC systems and known to  be more power
  consuming than Ivy Bridge successor.\\

\item \tinto is  a heterogeneous cluster composed of
  28 compute nodes at UJI. For our  experiments only a subset of 16 homogeneous nodes was considered. Each of them is composed dual-socket Intel Xeon E5645 hexa-core processors 
  running at 2.40\,GHz, equipped with 288\,GB  of DDR3 1333\,MHz and connected via Infiniband QDR with a Mellanox MTS3600 switch. A  full tracing  experiment is  conducted on
  \tinto in order to  capture an overall  power profile at a much
  finer resolution. In this sense, we also analyze the contribution of the MPI library
  to the energy consumption and how the use of the blocking versus polling
  message-passing policies can potentially render energy savings.
\end{itemize}

>>>>

\begin{itemize}
\item \monch is a 10 rack NEC-provided cluste rat CSCS composed
  of 312 compute  nodes. %and utilized by members  of the Swiss Platform
  %for Advanced Scientific  Computing (PASC) project~\citep{PASC}
  Each node comprises two Intel Ivy Bridge EP  E5-2660 ten-core processors
  operating at  2.2 GHz, equipped with 32\,GB of DDR3 1600\,MHz  RAM and connected  via InfiniBand Mellanox  SX6036 and FDR switches. For our  experiments, 
  a full rack constituted of 52 nodes was used. \monch is  slated to stay
  in  service  without  hardware  upgrade  for  the  duration  of  the
  Exa2Green  project,  allowing   an  identical  configuration  to  be
  recreated for future assessments of the baseline.\\

\item \pilat is a dual-socket eight-core Intel Sandy
  Bridge EP based cluster at  CSCS composed of 42 compute nodes. %and used as Piz Daint pre-post  processing cluster 
  The 2 login  nodes and
  the 42 computes nodes consists in 11 twin-pair Intel E5-Series DALCO
  r2264i4t 2U scalable compute modules. Each module contains 4 compute
  nodes based  on two Intel Xeon E5-2670 processors operating  at 2.6\,GHz equipped with 64GB of DDR3 1600\,MHz RAM and connected  via InfiniBand Mellanox SX6036 and FDR switches. 
  For our  experiments, a  full rack constituted  of 42 standard  compute nodes
  was used. \pilat  is based  on  Intel's second-generation
  processors, conventional in  HPC systems and known to  be more power
  consuming than Ivy Bridge successor.\\

\item \tinto is  a heterogeneous cluster composed of
  28 compute nodes at UJI. For our  experiments only a subset of 16 homogeneous nodes was considered. Each of them is composed dual-socket Intel Xeon E5645 hexa-core processors 
  running at 2.40\,GHz, equipped with 288\,GB  of DDR3 1333\,MHz and connected via Infiniband QDR with a Mellanox MTS3600 switch.

  % A  full tracing  experiment is  conducted on
  % \tinto in order to  capture an overall  power profile at a much
  % finer resolution. In this sense, we also analyze the contribution of the MPI library
  % to the energy consumption and how the use of the blocking versus polling
  % message-passing policies can potentially render energy savings.
\end{itemize}

### 2014-04-25 paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

OpenMPI 1.6.5, the communication library tested in \tinto, features two operation modes, 
blocking and modes, which can be selected when the application is launched.
In the polling configuration (the detault mode) ``MPI'' continually polls
the netwrok interface to check for the completion of an event (e.g. send or receive).
This usually yields low latency but high CPU utilization. Thus, can one expcet that this mode attanins the best performance, possibley at the cost a higher energy usage. In the blocking
mode, the CPU is yield to other processes/threads if there are no incoming messages.

>>>>

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. In this sense, we also analyze the contribution of the MPI library to the energy consumption and how the use of the blocking versus polling message-passing policies can potentially render energy savings.

Specifically, the OpenMPI 1.6.5 library leveraged in \tinto, features two operation modes, 
blocking and modes, which can be selected before \cosmoart is launched.
In the polling configuration (the detault mode) ``MPI'' continually polls
the netwrok interface to check for the completion of an event (e.g. send or receive).

This usually yields low latency but high CPU utilization. Thus, can one expcet that this mode attanins the best performance, possibley at the cost a higher energy usage. In the blocking
mode, the CPU is yield to other processes/threads if there are no incoming messages.
